---
title: "Policy simulation for Colombia"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 2
---

# Setup
```{r}
#--------------------------------------------------------------------------------
# Run anything of substance?
#--------------------------------------------------------------------------------
# Set default to FALSE, so it doesn't stall building the package
runNow <- TRUE
nsims <- 100

#-------------------------------------------------------------------------------
# Setup 
#-------------------------------------------------------------------------------
library(reshape)
library(parallel)
library(ggplot2)
library(knitr)
library(plyr)
library(bcimodel)
data(ex1)

#--------------------------------------------------------------------------------
# Knitr
#--------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```

# Set up inputs

## Initialize stats holder object

```{r, echo=TRUE}
#-------------------------------------------------------------------------------
# Stats will be contained in "val" list object
#-------------------------------------------------------------------------------
val <- vector('list', length=length(ex1))

#-------------------------------------------------------------------------------
# Statistics from Annals paper
#-------------------------------------------------------------------------------
propAdv <- 0.504
propERpos <- 0.42 
    # Will make this stage-specific later. 42% is Early. For Advanced, 40%.

# Convert 5-yr survivals to exponential rates
earlymort <- 0.01992 
advmort <- 0.10693
```


## Define policies to investigate

Note: baseline % advanced = `r 100*propAdv`%. 
```{r}
val$pol <- data.frame(num=c(1:4),
                         id=c('Y1977', 
                              'Y1999',
                              'Y1977.screening',
                              'Y1999.screening'
                              ),
                         name=c('1977 Control',
                                '1999 Control',
                                '1977 Screening',
                                '1999 Screening'),
                         pairnum=c(NA, NA, 1, 2),
                         earlydetHR=c(1, 1, 0.85, 0.85),
                         stringsAsFactors=FALSE)
kable(val$pol)
```

## Define natural history parameters

Advanced-stage is `r 100*propAdv`% and proportion ER+ is `r 100*propERpos`%. 

```{r}
val$nh <- compile_naturalhist(prop_adv=propAdv, 
                 mortrates=c(Early=earlymort, Advanced=advmort),
                 subgroup_probs=c(`ER+`=propERpos, `ER-`=1-propERpos))

# Change prop ER+ in advanced stage to 40%, not 42%
val$nh[val$nh$stage=='Advanced', 'prop'] <- c(0.40*propAdv, 0.60*propAdv)

kable(val$nh[,c('stage', 'subgroup', 'mortrate', 'prop')])
```


The "map" assigns numeric id's to each stage-subgroup. The stage-shifting will keep ER status constant, e.g. stage #3 shifts to #1 and stage #4 shifts to #2.
```{r}
(val$map <- create_stageshift_map(val$nh))
```

# Specify treatment for each policy

```{r}
# Annals treatments from breast_ER-HER2_6
annals_tx <- read.csv(system.file(file.path('extdata', 'validation', 
                                            'annals_treatment.csv'),
                                  package='bcimodel'))
# Remove the HER2- because for our purposes, they're duplications
val$tx <- subset(annals_tx, !grepl('HER2-', subgroup))
# Remove AI and Trastuzumab treatments
val$tx <- subset(val$tx, !grepl('AI', tx) & !grepl('Tras', tx))


ntreat <- nrow(val$tx)
ntx <- length(unique(val$tx$tx))

# Proportions sum to 1 within stage-subgroup groups
val$tx <- rename(val$tx, c('tx'='txSSid',
                           'HR'='txHR',
                           'prop_Y1977'='Y1977',
                           'prop_Y1999'='Y1999'))
val$tx <- transform(val$tx, 
                     SSno=c(rep(1,ntx), rep(2,ntx), rep(3,ntx), rep(4,ntx)),
                     SSid=c(rep('Early.ER+', ntx), rep('Advanced.ER+', ntx), 
                            rep('Early.ER-', ntx), rep('Advanced.ER-', ntx)), 
                     txSSno=1:ntreat,
                     Y1977.screening=Y1977,
                     Y1999.screening=Y1999)

# Proportions sum to 1
ddply(val$tx, .(SSno), summarise, s1977=sum(Y1977), s1999=sum(Y1999))

kable(val$tx)
```

# Incidence
```{r}
#-------------------------------------------------------------------------------
# TO DO 
#-------------------------------------------------------------------------------
data(incratesf)
theserates <- subset(incratesf,
                     Country %in% c('United States'))
plot_rates(theserates$Age, theserates$Female.Rate.Per.100K,
                      psize=theserates$Cases, 
                      group=paste(theserates$Country, theserates$Year))
```

# Results for US, no incidence trend
```{r, echo=TRUE}

if (runNow) {
    # Model
    startclock <- proc.time()
    manuscript_validation <- parsimpolicies(val$pol, val$nh, val$tx, 
                                          incsource='United States',
                                          mortsource='United States Birth Cohort 1950', 
                                          returnstats=c('mean', 'lower', 
                                                        'upper'), 
                                          futimes=c(10,25),
                                          minage=50, maxage=50, sims=nsims)
    # Runtime
    runtime_minutes <- (proc.time()-startclock)/60
    # Format and save results
    finaltab <- format_bounds_list(manuscript_validation, 
                                   paren=TRUE, includemean=TRUE, 
                                   digits=c(0,0,1,2,0,0),
                                   compileall=TRUE)
    write.csv(finaltab, file=paste0('validation_', nsims, 'sims.csv'), 
              row.names=FALSE)
}
```

## Runtime
Runtime in minutes:
```{r, echo=TRUE}
if (runNow) runtime_minutes
```

## Results
RESULTS FOR `r nsims` SIMS:

```{r}
if (runNow) kable(finaltab)
```

```{r, fig.height=10}
if (runNow) {
    rlong <- compile_long(manuscript_validation)
    rplot <- plot_results(rlong, type='line')
#    rplot
}
```

```{r, fig.height=10}
if (runNow) {
    rplot <- plot_results(rlong, type='bar')
#    rplot
}
```

# Results for US, with incidence trend
```{r, echo=TRUE}

if (runNow) {
    # Model
    startclock <- proc.time()
    manuscript_validation_withtrend <- parsimpolicies(val$pol, val$nh, val$tx, 
                                          incsource='United States times 1.005^20=1.1',
                                          mortsource='United States Birth Cohort 1950', 
                                          returnstats=c('mean', 'lower', 
                                                        'upper'), 
                                          futimes=c(10,25),
                                          minage=50, maxage=50, sims=nsims)
    # Runtime
    runtime_minutes <- (proc.time()-startclock)/60
    # Format and save results
    finaltab <- format_bounds_list(manuscript_validation_withtrend, 
                                   paren=TRUE, includemean=TRUE, 
                                   digits=c(0,0,1,2,0,0),
                                   compileall=TRUE)
    write.csv(finaltab, file=paste0('validation_withtrend_', nsims, 'sims.csv'), 
              row.names=FALSE)
}
```

## Runtime
Runtime in minutes:
```{r, echo=TRUE}
if (runNow) runtime_minutes
```

## Results
RESULTS FOR `r nsims` SIMS:

```{r}
if (runNow) kable(finaltab)
```

```{r, fig.height=10}
if (runNow) {
    rlong <- compile_long(manuscript_validation_withtrend)
    rplot <- plot_results(rlong, type='line')
#    rplot
}
```

```{r, fig.height=10}
if (runNow) {
    rplot <- plot_results(rlong, type='bar')
#    rplot
}
```
